Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-10-26 prop_letter.tex
Updates from ShareLaTeX

There are long-standing debates in the foundations of quantum
mechanics regarding the tension between finite precision measurement
and contextuality~\cite{BarrettKent2004,Appleby_2005}. The outcome of
a theory that is contextual depends upon whether compatible sets of
observables are measured together or separately; a non-contextual
theory gives the same results in either case.  A classic example of
the varying opinions on the impact of imprecision is the disagreement
between Meyer~\cite{PhysRevLett.83.3751} and Mermin~\cite{Mermin1999}
on whether finite-precision measurements invalidate the spirit of the
Kochen-Specker
theorem~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007,Held2016}.
The Kochen-Specker theorem is in essence a mathematical statement
about contextuality, asserting that in a Hilbert space of dimension
$d \ge 3$, it is impossible to associate definite probabilities,
$\mu(P_i)= 0$ or $1$, with every projection operator~$P_i$, in such a
way that, if a set of commuting $P_i$ satisfies $\sum_i P_i = 1$, then
$\sum_i \mu(P_i) = 1$.  Meyer showed that one {\it can\/} assign
definite probabilities $0$ or~$1$ to the measurement outcomes when the
Hilbert space is defined over the field of rational numbers, therefore
nullifying the theorem~\citep{PhysRevLett.83.3751}.  However, Mermin
then argued that measurement outcomes must depend smoothly on slight
changes in the experimental configuration, leading him to assert that
the impact of Meyer's negative result is
``unsupportable''~\citep{Mermin1999}.  The debate on whether
contextuality is consistent with experimental outcomes continues to be
an active topic of
research~\citep{Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.

@@

A principal result is that recasting the Kochen-Specker theorem in
terms of ``$\delta$-determinism'', with~$\delta$ quantifying the
effect of finite-precision uncertainties on measurement outcomes,
reducing to the purely deterministic Kochen-Specker case for
$\delta=0$, can resolve the question of the effect of finite precision
and imperfections on contextuality.  A remarkable consequence of our
analysis is that not only does the quantum-mechanical requirement for
contextuality continue to hold, thus maintaining the Kochen-Specker
result for a \emph{non-vanishing} range of $\delta$, but that at a
\emph{certain fixed value} of $\delta$, there is a sharp transition,
parallel in its consequences to, say, a phase transition, to
\emph{non-contextuality}; that is, suddenly a quantum system can be
simulated by a non-contextual hidden variable theory.
%% , turning the
%% system effectively from a quantum system into a classical system. 
% that is, quantum mechanics suddenly fails to hold, and all variables
% can be specified simultaneously, turning the theory effectively into a
% classical theory that can be specified consistently by hidden
% variables.
% \yutsung{The part after ``that is''
%   looks strange.
% \begin{enumerate}
% \item The Kochen-Specker theorem is not about quantum mechanics, is about whether
% quantum mechanics can be simulated by a non-contextual deterministic hidden
% variable theory or not. Hence, ``quantum mechanics suddenly fails to hold''
% doesn't make a lot sense.
% \item The question is whether there exist a QIVPM means ``a classical theory
% consistently by hidden variables.'' At least, a QIVPM is not deterministic, and
% I need to check whether it qualities as a classical probabilistic hidden variable
% theory\ldots(?)
% \end{enumerate}
% }
%% \yutsung{Still not comfortable about the current statement...}
These results provide a new insight into the Meyer-Mermin debate by
presenting a theory in which there is a \emph{parameter} interpolating
between what appeared previously to be irreconcilable interpretations
of contextuality.

We also investigate the second key aspect of imprecise quantum
measurement, which is its statistical nature as reflected in the
application of the Born rule determining the probability of a given
measurement outcome~\citep{Born1983,peres1995quantum,544199}.  Here,
Gleason's theorem establishes that there is no alternative to the Born
rule by demonstrating, using reasonable continuity arguments in
Hilbert spaces of dimension $d\ge3$, the existence of a unique state
$\rho$ consistent with the statistical predictions computed from that
rule~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.  Our
question then concerns what happens when infinite precision cannot be
achieved.  We are able to show that, while a QIVPM incorporating the
effects of finite precision might not be consistent with Gleason's
unique state~$\rho$ on all projectors defined on a Hilbert space
$\Hilb$ of dimension $d\ge3$, there is a mathematically precise sense
in which one recovers the original Gleason theorem asymptotically.
Specifically, it is possible to construct a class of QIVPMs
representing bounded resources that is parameterized by the size of
the probability intervals of uncertainty. We then demonstrate that all
QIVPMs in this class are consistent with a non-empty set of quantum
states, and as the size of the intervals characterizing the
uncertainties goes to zero, this set of quantum states converges to
the unique state consistent with the Born rule. We furthermore
establish a mathematical correlation between the sizes of the
intervals and the volume of states that are all consistent with an
imprecise measurement.

@@

We will start by reviewing IVPMs in the classical setting and then
propose our quantum generalization. In the classical setting, there
are several proposals for ``imprecise
probabilities''~\citep{Dempster1967,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
Although these proposals differ in some details, they all share the
fact that the probability $\mu(E)$ of an event~$E$ is generalized from
a single \emph{real number} to an \emph{interval}~$[\ell,r]$
where~$\ell$ intuitively corresponds to the strength of evidence for
the event~$E$ and~$1-r$ corresponds to the strength of evidence
against the same event. Under some additional assumptions, this
interval could be interpreted as the Gaussian width of a probability
distribution. We use general intervals with no constraints other than
the ones needed to maintain coherence: these are described next.

@@

Let $E_1$ and $E_2$ be two disjoint events with probabilities
$\mu(E_1)=[\ell_1,r_1]$ and $\mu(E_2)=[\ell_2,r_2]$. A first attempt
at calculating the probability of the combined event that
\emph{either} $E_1$ or $E_2$ occurs might be
$\mu(E_1\cup E_2) = [\ell_1+\ell_2,r_1+r_2]$. In some cases, this is
indeed a sensible definition. For example, if $\mu(E_1)=[0.1,0.2]$ and
$\mu(E_2)=[0.3,0.4]$ we get $\mu(E_1\cup E_2) = [0.4,0.6]$. But
consider an event $E$ such that $\mu(E)=[0.2,0.3]$ and hence
$\mu(\overline{E})=[0.7,0.8]$. The two events $E$ and $\overline{E}$
are disjoint; the naïve addition of intervals would give
$\mu(E\cup\overline{E})=[0.9,1.1]$ which is not a valid probability
interval. Moreover the event $E\cup\overline{E}$ is the
entire space; its probability interval should be
$\necess$ which is sharper than $[0.9,1.1]$. The problem is that the
two intervals are correlated: there is more information in the
combined event than in each event separately. In our example, even
though the ``true'' probability of $E$ can be anywhere in the range
$[0.2,0.3]$ and the ``true'' probability of~$\overline{E}$ can be in
anywhere in the range $[0.7,0.8]$, the values are not independent. Any
value of $\mu(E) \leq 0.25$ will force $\mu(\overline{E})\geq
0.75$. To account for such subtleties, the axioms of interval-valued
probability do not use a strict equality for the combination of
disjoint events. The correct constraint regarding the probability of
$E_1\cup E_2$ when $E_1$ and $E_2$ are disjoint is
$\mu(E_1\cup E_2) \subseteq [\ell_1+\ell_2,r_1+r_2]$ which, in
combination with the requirement for the event of the entire space would force
$\mu(E \cup \overline{E})$ to always be $\necess$ irrespective of the
particular assignments of $\mu(E)$ or~$\mu(\overline{E})$. 
%% Parallel arguments
%% can be made interpreting $[\ell,r]$ as Gaussian width, but will be omitted as no
%% essential new information seems to be introduced.

@@

We now have the necessary ingredients to define the quantum extension,
QIVPMs, as a generalization of both classical IVPMs and conventional
quantum probability measures. We will show that QIVPMs reduce to
classical IVPMs when the space of quantum events is restricted to
mutually commuting events, i.e., to compatible events that can be
measured simultaneously. In Sec.~\ref{sec:Gleason} we will discuss the
connection between QIVPMs and conventional quantum probability
measures in detail.

@@

For example, a well-defined  
QIVPM, assuming the three intervals $\imposs$, $\necess$, and
$\unknown=\left[0,1\right]$, is:
\begin{equation}
\bar{\mu}_{1}\left(P\right)=\begin{cases}
\imposs\,, & \text{if }P=\mathbb{0}\text{ ;}\\
\necess\,, & \text{if }P=\mathbb{1}\text{ ;}\\
\unknown\,, & \text{otherwise.}
\end{cases}\label{eq:no-information-IVPM}
\end{equation}
This measure represents the beliefs of an experimenter with no prior
knowledge about the particular quantum system in question; any quantum
state would be consistent with $\bar{\mu}_{1}$ on any projectors, and
$\coreBorn\left(\bar{\mu}_{1},\events\right)$ is just the set of all
states. The subspace
$\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
is a subspace of commuting events. Indeed restricting $\bar{\mu}_{1}$
to $\events_{0}$, $\bar{\mu}_{1}|_{\events_{0}}$, gives a classical
IVPM~$\bar{\mu}_{2}$:
\begin{equation}
\begin{aligned}\bar{\mu}_{2}(\mathbb{0}) & =\imposs & \bar{\mu}_{2}(\proj{0}) & =\unknown\\
\bar{\mu}_{2}(\mathbb{1}) & =\necess & \bar{\mu}_{2}(\proj{1}) & =\unknown
\end{aligned}
\label{eq:classical-no-information-IVPM}
\end{equation}
If we identify the states ~$\proj{0}$ and $\proj{1}$ with the head and
the tail of a coin, respectively, then $\bar{\mu}_{2}$ represents the
situation in which an experimenter knows nothing about a coin before
she tosses it. Moreover, for each $p\in\left[0,1\right]$, the
state~$p\proj{0}+\left(1-p\right)\proj{1}$ represents a classical coin
with probability~$p$ to get heads, and
$p\proj{0}+\left(1-p\right)\proj{1}$ is consistent
with~$\bar{\mu}_{2}$ on $\events_{0}$ because any classical coin
should be consistent with the situation for which an experimenter has
no prior knowledge.

@@

\noindent Intuitively the expectation value of an observable relative
to a QIVPM $\bar{\mu}$ lies between two possible outcomes, which
themselves lie between the minimum and maximum bounds of the
probability intervals associated with each state~$\rho$ that is
consistent with~$\bar{\mu}$ on every projector in the spectral
decomposition of the observable. If $\bar{\mu}$ is a conventional
(Born) probability measure induced by a state $\rho$, then the Born
rule probability induced by every state in
$\coreBorn\left(\bar{\mu},\events'\right)$ will be
$\mu_{\rho}^{\mathrm{B}}$ and the interval collapses to a point, thus
reducing the definition to that of
Eq.~(\ref{eq:quantum-expectation})~\citep{HOSTunpublished}.
% For example, we can extend one of the fragments of valid probability
% measures~$\mu_{1}$ defined in Table~\ref{tab:quantum-probability-measure}
% to a QIVPM~$\bar{\mu}_{3}$:
% \begin{equation}
% \begin{aligned}\bar{\mu}_{3}(\proj{0}) & =\left[\tfrac{1}{2},\tfrac{1}{2}\right] & \bar{\mu}_{3}(\proj{2}) & =\left[0,0\right]\\
% \bar{\mu}_{3}(\proj{1}) & =\left[\tfrac{1}{2},\tfrac{1}{2}\right] &  & \ldots\textrm{ etc.}
% \end{aligned}
% \label{eq:Born-QIVPM}
% \end{equation}
% For the same observable~$\mathbf{O}=\proj{0}+2\,\proj{1}+3\,\proj{2}$,
% the only state~$\rho$ consistent with $\bar{\mu}_{3}$ on $\proj{0}$,
% $\proj{1}$, and $\proj{2}$ must be $\proj{\ps}$, and $\mu_{1}=\mu_{\proj{\ps}}^{\mathrm{B}}$.
% Therefore, the expectation value~$\expval{\mathbf{O}}_{\bar{\mu}_{3}}=\left[\expval{\mathbf{O}}_{\mu_{1}},\expval{\mathbf{O}}_{\mu_{1}}\right]=\left[1.5,1.5\right]$
% which is an interval, but not between $0$ and $1$ because it is
% not a probability of an event. 
We also note that, when restricted to commuting projectors, the
definition above is consistent with the classical notion of the
\emph{Choquet integral}~\citep{GilboaSchmeidler1994,Grabisch2016}
which is used to calculate the expectation value of random variables
as a weighted average~\citep{HOSTunpublished}.

>>>>

There are long-standing debates in the foundations of quantum
mechanics regarding the tension between finite precision measurement
and contextuality~\cite{BarrettKent2004,Appleby_2005}. The outcome
of a theory that is contextual depends upon
whether  compatible sets of observables are measured together or
separately; a non-contextual theory gives the same results in either
case.  A classic example of the varying opinions on the impact of
imprecision is the disagreement between
Meyer~\cite{PhysRevLett.83.3751} and 
Mermin~\cite{Mermin1999}  on whether finite-precision
measurements invalidate the spirit of the Kochen-Specker
theorem~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007,Held2016}.  The Kochen-Specker  
theorem is in essence a
mathematical statement about contextuality, asserting that
in a Hilbert space of dimension $d \ge 3$, it is
impossible to associate definite measured values, $\mu(P_i)= 0$ or
$1$, with every projection operator~$P_i$, in such a way that, if a
set of commuting $P_i$ satisfies $\sum_i P_i = 1$, then
$\sum_i \mu(P_i) = 1$.   Meyer showed that one {\it can\/}
assign definite values $0$ or~$1$ to the measurement outcome
$\mu(P_i)$ when the Hilbert space is defined over the field of
rational numbers, therefore nullifying the
theorem~\citep{PhysRevLett.83.3751}.  However, Mermin then argued
that measurement outcomes must depend smoothly on slight changes in
the experimental configuration, leading him to assert that the
impact of Meyer's negative result is
``unsupportable'' on physical grounds ~\citep{Mermin1999}.  The debate on
whether contextuality is consistent with experimental
outcomes continues to be an active topic of research~\citep{Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.

@@

A principal result is that recasting the Kochen-Specker theorem in
terms of ``$\delta$-determinism'', with~$\delta$ quantifying the
effect of finite-precision uncertainties on measurement outcomes,
reducing to the purely deterministic Kochen-Specker case for
$\delta=0$, can resolve the question of the effect of finite precision
and imperfections on contextuality.  A remarkable consequence of our
analysis is that not only does the quantum-mechanical requirement for
contextuality continue to hold, thus maintaining the Kochen-Specker
result for a \emph{non-vanishing} range of $\delta$, but that at a
\emph{certain fixed value} of $\delta$, there is a sharp transition,
parallel in its consequences to, say, a phase transition, to
\emph{non-contextuality}; that is, suddenly a quantum system can be
simulated by a non-contextual hidden variable theory, turning the
system effectively from a quantum system into a classical system. 
% that is, quantum mechanics suddenly fails to hold, and all variables
% can be specified simultaneously, turning the theory effectively into a
% classical theory that can be specified consistently by hidden
% variables.
% \yutsung{The part after ``that is''
%   looks strange.
% \begin{enumerate}
% \item The Kochen-Specker theorem is not about quantum mechanics, is about whether
% quantum mechanics can be simulated by a non-contextual deterministic hidden
% variable theory or not. Hence, ``quantum mechanics suddenly fails to hold''
% doesn't make a lot sense.
% \item The question is whether there exist a QIVPM means ``a classical theory
% consistently by hidden variables.'' At least, a QIVPM is not deterministic, and
% I need to check whether it qualities as a classical probabilistic hidden variable
% theory\ldots(?)
% \end{enumerate}
% }
\yutsung{Still not comfortable about the current statement...}
These results provide a new insight into the Meyer-Mermin debate by
presenting a theory in which there is a \emph{parameter} interpolating
between what appeared previously to be irreconcilable interpretations
of contextuality.

We also investigate, though with less insight-generating results, the
second key aspect of imprecise quantum measurement, which is its
statistical nature as reflected in the application of the Born rule
determining the probability of a given measurement
outcome~\citep{Born1983,peres1995quantum,544199}.  Here, Gleason's
theorem establishes that there is no alternative to the Born rule by
demonstrating, using reasonable continuity arguments in Hilbert spaces
of dimension $d\ge3$, the existence of a unique state $\rho$
consistent with the statistical predictions computed from that
rule~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.  Our
question then concerns what happens when infinite precision cannot be
achieved.  We are able to show that, while a QIVPM incorporating the
effects of finite precision might not be consistent with Gleason's
unique state~$\rho$ on all projectors defined on a Hilbert space
$\Hilb$ of dimension $d\ge3$, there is a mathematically precise sense
in which one recovers the original Gleason theorem asymptotically.
Specifically, if a set of QIVPMs representing bounded resources
correspond individually to at least one state's~$\rho'$, those states
will converge to a unique state $\rho$ in the limit as the size of the intervals
characterizing the uncertainties goes to zero, and the set of
single-point QIVPMs densely covers the entire real interval $[0,1]$ or the
appropriate subset corresponding to a given quantum system.

@@

We will start by reviewing IVPMs in the classical setting and then
propose our quantum generalization. In the classical setting, there
are several proposals for ``imprecise
probabilities''~\citep{Dempster1967,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
Although these proposals differ in some details, they all share the
fact that the probability $\mu(E)$ of an event~$E$ is generalized from
a single \emph{real number} to an \emph{interval}~$[\ell,r]$
where~$\ell$ intuitively corresponds to the strength of evidence for
the event~$E$ and~$1-r$ corresponds to the strength of evidence
against the same event. More generally, this inverval would be interpreted as
the Gaussian width of a probability distribution, but for notational
convenience we will continue in the following to write this as a definite interval.
\yutsung{Check the interpretation in the statistics literature~\citep{HuberRonchetti2009}!
Or we may need to prove it could be interpreted as Guassian width
by ourselves...} The collection of intervals used in the
definition of a probability measure must satisfy certain properties
that we explain next.

@@

Let $E_1$ and $E_2$ be two disjoint events with probabilities
$\mu(E_1)=[\ell_1,r_1]$ and $\mu(E_2)=[\ell_2,r_2]$. A first attempt
at calculating the probability of the combined event that
\emph{either} $E_1$ or $E_2$ occurs might be
$\mu(E_1\cup E_2) = [\ell_1+\ell_2,r_1+r_2]$. In some cases, this is
indeed a sensible definition. For example, if $\mu(E_1)=[0.1,0.2]$ and
$\mu(E_2)=[0.3,0.4]$ we get $\mu(E_1\cup E_2) = [0.4,0.6]$. But
consider an event $E$ such that $\mu(E)=[0.2,0.3]$ and hence
$\mu(\overline{E})=[0.7,0.8]$. The two events $E$ and $\overline{E}$
are disjoint; the naïve addition of intervals would give
$\mu(E\cup\overline{E})=[0.9,1.1]$ which is not a valid probability
interval. Moreover the event $E\cup\overline{E}$ is the
entire space; its probability interval should be
$\necess$ which is sharper than $[0.9,1.1]$. The problem is that the
two intervals are correlated: there is more information in the
combined event than in each event separately. In our example, even
though the ``true'' probability of $E$ can be anywhere in the range
$[0.2,0.3]$ and the ``true'' probability of~$\overline{E}$ can be in
anywhere in the range $[0.7,0.8]$, the values are not independent. Any
value of $\mu(E) \leq 0.25$ will force $\mu(\overline{E})\geq
0.75$. To account for such subtleties, the axioms of interval-valued
probability do not use a strict equality for the combination of
disjoint events. The correct constraint regarding the probability of
$E_1\cup E_2$ when $E_1$ and $E_2$ are disjoint is
$\mu(E_1\cup E_2) \subseteq [\ell_1+\ell_2,r_1+r_2]$ which, in
combination with the requirement for the event of the entire space would force
$\mu(E \cup \overline{E})$ to always be $\necess$ irrespective of the
particular assignments of $\mu(E)$ or~$\mu(\overline{E})$. Parallel arguments
can be made interpreting $[\ell,r]$ as Gaussian width, but will be omitted as no
essential new information seems to be introduced.

@@

We now have the necessary ingredients to define the quantum extension,
QIVPMs, as a generalization of both classical IVPMs and quantum
probability measures. We will show that QIVPMs reduce to classical
IVPMs when the space of quantum events is restricted to mutually
commuting events, i.e., to compatible events that can be measured
simultaneously. In Sec.~\ref{sec:Gleason} we will discuss the
connection between QIVPMs and conventional quantum probability
measures.

@@

For example, a well-defined  
QIVPM, assuming the three intervals $\imposs$, $\necess$, and
$\unknown=\left[0,1\right]$, is:
\begin{equation}
\bar{\mu}_{1}\left(P\right)=\begin{cases}
\imposs\,, & \text{if }P=\mathbb{0}\text{ ;}\\
\necess\,, & \text{if }P=\mathbb{1}\text{ ;}\\
\unknown\,, & \text{otherwise.}
\end{cases}\label{eq:no-information-IVPM}
\end{equation}
This measure represents the beliefs of an experimenter with no prior
knowledge about the particular quantum system in question; any quantum
state would be consistent with $\bar{\mu}_{1}$ on any projectors, and
$\coreBorn\left(\bar{\mu}_{1},\events\right)$ is just the set of all
states. The subspace
$\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
is a subspace of commuting events. Indeed restricting $\bar{\mu}_{1}$
to $\events_{0}$, $\bar{\mu}_{1}|_{\events_{0}}$, gives a classical
IVPM~$\bar{\mu}_{2}$:
\begin{equation}
\begin{aligned}\bar{\mu}_{2}(\mathbb{0}) & =\imposs & \bar{\mu}_{2}(\proj{0}) & =\unknown\\
\bar{\mu}_{2}(\mathbb{1}) & =\necess & \bar{\mu}_{2}(\proj{1}) & =\unknown
\end{aligned}
\label{eq:classical-no-information-IVPM}
\end{equation}
If we identify the states ~$\proj{0}$ and $\proj{1}$ with the head
and the tail of a coin, respectively, then $\bar{\mu}_{2}$ represents
the situation in which an experimenter knows nothing about a coin
before she tosses it. Moreover, for each $p\in\left[0,1\right]$, the
state~$p\proj{0}+\left(1-p\right)\proj{1}$ represents a classical
coin with probability~$p$ to get heads, and
$p\proj{0}+\left(1-p\right)\proj{1}$ is consistent with
$\bar{\mu}_{2}$ on $\events_{0}$ because any classical coin should be
consistent with the situation for which an experimenter has no prior
knowledge.

@@

\noindent Intuitively the expectation value of an observable relative
to a QIVPM $\bar{\mu}$ lies between two possible outcomes, which
themselves lie between the minimum and maximum bounds of the probability
intervals associated with each state~$\rho$ that is consistent with
$\bar{\mu}$ on every projector in the spectral decomposition of the
observable. If $\bar{\mu}$ is a conventional (Born) probability measure
induced by a state $\rho$, then the Born rule probability induced
by every state in $\coreBorn\left(\bar{\mu},\events'\right)$ will
be $\mu_{\rho}^{\mathrm{B}}$ and the interval collapses to a point,
thus reducing the definition to that of Eq.~(\ref{eq:quantum-expectation})~\citep{HOSTunpublished}.
For example, we can extend one of the fragments of valid probability
measures~$\mu_{1}$ defined in Table~\ref{tab:quantum-probability-measure}
to a QIVPM~$\bar{\mu}_{3}$:
\begin{equation}
\begin{aligned}\bar{\mu}_{3}(\proj{0}) & =\left[\tfrac{1}{2},\tfrac{1}{2}\right] & \bar{\mu}_{3}(\proj{2}) & =\left[0,0\right]\\
\bar{\mu}_{3}(\proj{1}) & =\left[\tfrac{1}{2},\tfrac{1}{2}\right] &  & \ldots\textrm{ etc.}
\end{aligned}
\label{eq:Born-QIVPM}
\end{equation}
For the same observable~$\mathbf{O}=\proj{0}+2\,\proj{1}+3\,\proj{2}$,
the only state~$\rho$ consistent with $\bar{\mu}_{3}$ on $\proj{0}$,
$\proj{1}$, and $\proj{2}$ must be $\proj{\ps}$, and $\mu_{1}=\mu_{\proj{\ps}}^{\mathrm{B}}$.
Therefore, the expectation value~$\expval{\mathbf{O}}_{\bar{\mu}_{3}}=\left[\expval{\mathbf{O}}_{\mu_{1}},\expval{\mathbf{O}}_{\mu_{1}}\right]=\left[1.5,1.5\right]$
which is an interval, but not between $0$ and $1$ because it is
not a probability of an event. We also note that, when restricted
to commuting projectors, the definition above is consistent with the
classical notion of the \emph{Choquet integral}~\citep{GilboaSchmeidler1994,Grabisch2016}
which is used to calculate the expectation value of random variables
as a weighted average~\citep{HOSTunpublished}.
